---
title: "p8105_hw1_ht2630"
author: "Haotian Tang"
date: "`r Sys.Date()`"
output: github_document
---

This is homework 1. 

___

Problem 1

```{r}

library(moderndive)

data("early_january_weather")

?early_january_weather

weather = early_january_weather

colnames(weather)

ncol(weather)

nrow(weather)

temp = weather$temp

mean(temp)

library(tidyverse)

time_hour = weather$time_hour

ggplot(weather, 
       aes(x = time_hour, y = temp, color = humid)) + 
  geom_point() +
  xlab("Date and Time") + 
  ylab("Temperature")

ggsave("p8105_hw1_ht2630_ggplot.jpg")
```

We can see there are 15 columns and 358 rows. The variables are shown in the first result. 

According to the section of "Help",

"temp" is the temperature. 

"dewp" is the dew point. 

"wind_dir", "wind_speed", and "wind_gust" are wind derection, speed and gust speed. 

"precip" is the precipitation. 

"visib" is the visibility. 

"time_hour" is the data and hour of recording. 

The last section shows the mean temperature is 39.58212. 

The ggplot shows that temperature has some fluctuation across the time but a increasing trend is observed.  

---

Problem 2

```{r}

data_frame = tibble(
  random_sample = rnorm(10), 
  logical_vector = random_sample > 0,
  character_vector = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vector = factor(c("Level1", "Level1", "Level1", "Level2", "Level2", "Level2", "Level3", "Level3", "Level3", "Level3"))
)

mean(pull(data_frame, random_sample))

mean(pull(data_frame, logical_vector))

mean(pull(data_frame, character_vector))

mean(pull(data_frame, factor_vector))

```

```{r, echo = FALSE, results='hide'}

as.numeric(data_frame$logical_vector)

as.numeric(data_frame$character_vector)

as.numeric(data_frame$factor_vector)

```
Thus, we can find that we can take means from the random sample and logical vector, 

but not from character vector and factor vector. 

When we use as.numeric function to the last three vectors, 

we can find the logical vector shows 1 and 0, which explains why it has mean. 

The mean is just the frequency of TRUE. 

The as.numeric function of character vector shows NA, 

so it is not numeric and it does not have mean. 

However, we can find the as.numeric function of the factor vector shows 1, 2, and 3,

which does not why the factor vector does not have mean. 

Therefore, it partially explains which of them have the mean. 


